Untrusted B2B Collaboration using the Blockchain

### 2018-07-31 paper/paper.tex
Fix possesive

In our implementation, a companys factory contract also knows the address of the companys access contract for convenience.
Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e. an ID that is shared between all choreography participants for each instance of the shared choreography.

@@

A factory contract thus has the resulting interface:
\begin{itemize}
	\item A \texttt{constructor} where the address of the companys access contract is passed
	\item Setter methods for the factory contract addresses of interaction partners
	\item A \texttt{createInstance} function
	\item A \texttt{getAccessAddress} function
	\item A \texttt{isInstance} function used to verify whether an address points to an instance contract created by this factory (for a given choreography ID)
\end{itemize}

@@

Communication between smart contracts happens in the form of function calls.
To allow the factory and instance contracts to call functions on their interaction partners contracts, the partners function interface needs to be known, i.e. it needs to be declared in the factory contract source code.
%- the access contract (same for every participant)
%- remote factory contracts (if receiving messages from remote, for verification)
%- remote instance contracts (if sending messages to remote instance)

The instance contract definition is also part of the factory contract source code.
The factory contract creates an instance by calling its constructor and passing all addresses that are required for the inter-process communication .
Instance contracts provide functions for each sending action, i.e. send tasks or events in the companys process, which can be called by the process engine.
For each receiving action (task or event), a function needs to be present that can be called from other instance contracts.
When company $A$ triggers a sending function on their instance contract, it in turn calls a corresponding receive function on the instance contract of company $B$.

Instance contracts need to store:
\begin{itemize}
	\item The choreography instance ID for verifying incoming messages
	\item The addresses of the factory and access contracts of partners for verifying incoming messages
	\item The addresses of the instance contracts of partners for sending messages
	\item The address of the companys own access contract, for verifying local function calls
	\item The address of the companys own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
\end{itemize}

Verification is implemented on sender side and on receiver side.
Each send function has a guard checking the caller in the companys own access contract.
Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partners access contract.
Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in~\cite{xu2018pattern}.

@@

Each company deploys an access contract that holds information about the roles and permissions of the companys employees.
Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from~\cite{xu2018pattern}.
It allows decoupling the roles and permissions from the actual contract instances, allowing for a simple modification at runtime.
Access contracts can be deployed per process, or even once per company as a single source of truth for all processes.

@@

Most of the implementation can be generated, e.g. from a choreography diagram (or at least from the participants public processes).
The next step is to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments.
Given such a template, one can work on a contract generation tool that takes a diagram as input and produces factory contract code.
A possible implementation could use a rule-based approach for translating the choreography model, similar to~\cite{lopez2017caterpillar}.

>>>>

In our implementation, a company's factory contract also knows the address of the company's access contract for convenience.
Additionally, it stores the addresses of created instances, mapped by a \emph{choreography instance ID}, i.e. an ID that is shared between all choreography participants for each instance of the shared choreography.

@@

A factory contract thus has the resulting interface:
\begin{itemize}
	\item A \texttt{constructor} where the address of the company's access contract is passed
	\item Setter methods for the factory contract addresses of interaction partners
	\item A \texttt{createInstance} function
	\item A \texttt{getAccessAddress} function
	\item A \texttt{isInstance} function used to verify whether an address points to an instance contract created by this factory (for a given choreography ID)
\end{itemize}

@@

Communication between smart contracts happens in the form of function calls.
To allow the factory and instance contracts to call functions on their interaction partner's contracts, the partner's function interface needs to be known, i.e. it needs to be declared in the factory contract source code.
%- the access contract (same for every participant)
%- remote factory contracts (if receiving messages from remote, for verification)
%- remote instance contracts (if sending messages to remote instance)

The instance contract definition is also part of the factory contract source code.
The factory contract creates an instance by calling its constructor and passing all addresses that are required for the inter-process communication .
Instance contracts provide functions for each sending action, i.e. send tasks or events in the company's process, which can be called by the process engine.
For each receiving action (task or event), a function needs to be present that can be called from other instance contracts.
When company $A$ triggers a sending function on their instance contract, it in turn calls a corresponding receive function on the instance contract of company $B$.

Instance contracts need to store:
\begin{itemize}
	\item The choreography instance ID for verifying incoming messages
	\item The addresses of the factory and access contracts of partners for verifying incoming messages
	\item The addresses of the instance contracts of partners for sending messages
	\item The address of the company's own access contract, for verifying local function calls
	\item The address of the company's own factory contract, for returning any remaining funds upon \texttt{selfdestruct}
\end{itemize}

Verification is implemented on sender side and on receiver side.
Each send function has a guard checking the caller in the company's own access contract.
Each receive function has a guard checking a) that the caller is a contract instance that is part of the choreography instance (via the partner factory contract), and b) checking the account behind the request in the partner's access contract.
Guarding functions against unwanted access was described in pattern 13, Embedded Permission, in~\cite{xu2018pattern}.

@@

Each company deploys an access contract that holds information about the roles and permissions of the company's employees.
Having permission data encapsuled in a separate access contract follows pattern 12, the Data Contract pattern, from~\cite{xu2018pattern}.
It allows decoupling the roles and permissions from the actual contract instances, allowing for a simple modification at runtime.
Access contracts can be deployed per process, or even once per company as a single source of truth for all processes.

@@

Most of the implementation can be generated, e.g. from a choreography diagram (or at least from the participant's public processes).
The next step is to define a template for the factory contract source code, to determine which parts are easily generated, and which parts might need manual adjustments.
Given such a template, one can work on a contract generation tool that takes a diagram as input and produces factory contract code.
A possible implementation could use a rule-based approach for translating the choreography model, similar to~\cite{lopez2017caterpillar}.
